Estimation below the detection limit

### 2018-03-12 TEX/draft1.tex
Updated notes

This work is primely motivated by the challenging $\SNR$ levels being manifested in  innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL). The acquired data in these technologies suffers from very high noise level.  In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.

If the noise level is negligible, estimating the signals is easy.
One can detect the signal occurrences in the data sequence and then estimate the signals using clustering and averaging.
Even in higher noise level regimes, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible. In Figure~\ref{fig:example} we demonstrate an instance of the problem in different noise levels. Figure~\ref{fig:data2D_clean} shows a excerpt of a big image that contains many repetitions of $21\times 21$ small image. The small image is a downsampled version of TKTK, which is shown in Figure~\ref{fig:signal2D_clean}. In Figures~\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} the same excerpt is shown with the addition of i.i.d.\ Gaussian noise with standard deviation of $0.2$ and $1$, respectively.

@@

	\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{signal2D_clean}
	\caption{Clean signal}
	\label{fig:signal2D_clean}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{signal2D_LS}
	\caption{Recovered signal using LS}
	\label{fig:signal2D_LS}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{signal2D_RRR}
	\caption{This one will be replaced}
	\label{fig:signal2D_RRR}
\end{subfigure}

@@

@@

Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the measurement. For each $x_i$, let $s_i\in\{0,1\}^N$ be a binary signal, referred to as the \emph{support signal}. The non-zero values of $s_i$ indicates the locations of $x_i$ in $y$. If $s_i[n]=1$, then $y[n+j] = x_i[n+j]+\varepsilon[n+j]$ for $j=0,\ldots,L-1$. The further denote $s = \sum_{i=1}^Ks_i$ as the union of supports.

The support signals are generated by the following generative model. First, an index $i_1$ is drawn uniformly from $\{1,\ldots,N\}$. A second index $i_2$ is drawn uniformly from $\{1,\ldots,N\}$. If $\vert i_2-i_1\vert \geq L-1$,
then we set $s[i_2]=1$, otherise we keep $s[i_2]=0$ and draw an index again. We proceed to add non-zero entries to $s$ while keeping the separation condition. This process is halted when the number of when support is full enough by some predefined criterion. Once the signal $s$ is determined, for each non-zero entries is drawn from $\{1,\ldots,K\}$ and associated with the chosen signal. We note that if the support is sparse enough, this generative model can be approximated by a simpler process that ignores the separation constraint and simply choose $m$ random location in uniform over $\{1,\ldots N\}$. The number of occurrences $m_i,\ldots,m_K$ is unknown to us.

The simplest way to present the forward model is a blind deconvolution problem between the support signals and the unknown signals
\begin{equation}
y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
\end{equation}
We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
The goal is to estimate $x1,\ldots,x_K$ from $y$.

Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few. Clearly, without additional information on the signal, blind deconvolution is ill-posed. In our case, the prior information is that $s$ is a binary, sparse, signal. 
Other settings of blind deconvolution problems have been analyzed recently under different settings, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
where the focus is on the high \SNR regime.

If $x$ is known and $K=1$, then  $s$ can be estimated by linear program in high \SNR~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}. However, in the low \SNR regime, estimating $s$ is impossible. To see that, suppose that for each non-zero value of $s$, an oracle provides you 
a window that contains it. Namely, we get a series of windows, each one contains a signal at unknown location. The question is whether one can estimate the locations of the signals within the windows. Apparently, this cannot be done. For instance, the variance of any estimator is, at best, proportional to $\sigma^2$ and independent of the number of windows, even if $x$ is known~\cite{aguerrebere2016fundamental}.  Since this alignment problem is essentially easier then the problem under consideration, we conclude that detecting the non-zero values of $s$ is impossible in low \SNR. In our setup, $s$ is the \emph{latent} variable of the problem. Indeed, in many blind deconvolution applications the goal is merely to estimate one of the unknown signals. For instance, in image deblurring, both the blurring
kernel and the high-resolution image are unknown, but the prime goal is only
to sharpen the image.
In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any $\SNR$ level and to any accuracy, although we cannot estimate their occurrences.

@@

Our method for estimating the signals relies on two pillars. 
First, we use the autocorrelation functions of the data to estimate a mix (i.e., linear combination) of the signals autocorrelations. The mixed autocorrelation can be estimated to any accuracy, in any \SNR level, if $M$ is large enough. Then, we use least-squares (LS) estimator to estimate the signals from their mixed autocorrelation.

For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions, defined as
\begin{align} \label{eq:autocorrelations}
a_y^1 &= \sum_{i=0}^{N-1} y[i], \nonumber\\
a_y^2[\ell] &= \sum_{i=0}^{N-1-\ell} y[i]y[i+\ell], \nonumber\\
a_y^3[\ell_1,\ell_2] &= \sum_{i=0}^{N-1-\max\{\ell_1,\ell_2\}} y[i]y[i+\ell_1]y[i+\ell_2]. 
\end{align}
Note that the autocorrelation functions are symmetric so that $a_y^2[\ell] = a_y^2[-\ell]$ and $a_y^3[\ell_1,\ell_2] = a_y^3[-\ell_1,-\ell_2]$.

The analysis of the autocorrelations is conducted in the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$. We define the ratios 
\begin{equation}
\gamma_i = \frac{M_i L}{N},
\end{equation}
and $\gamma = \sum_{i=1}^K\gamma_i$.
Under the separation condition, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
If $s$ satisfies the separation condition, then the first $L$ entries of the data autocorrelations converge to a $\gamma$ scaled version of a mix of the signals autocorrelations:
\begin{align}
\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \\
\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]),
\end{align}
for $\ell,\ell_1,\ell_2=0,\ldots L-1$.
These relations are proved in Appendix~\ref{sec:autocorrelation_computation}. The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a special caution should be taken with the noise dependencies.

The third order autocorrelation defines the signals uniquely. For $K=1$, we have the following simple result:
\begin{proposition}
	Suppose that $x[0]$ and $x[L-1]$ are non-zeros. Then, the signal is determined uniquely from  $a_x^2$ and $a_x^3$.
	\begin{proof}
From the second-order autocorrelation, we ge
\begin{equation*}
a_x^2[L-1] = x[0]x[L-1]\neq 0.
\end{equation*}
Then, from the third-order autocorrelation we can compute $x[k]$ for all $k=0,\ldots L-1$ by
\begin{eqnarray}
a_x^3[k,L-1] = x[0]x[k]x[L-1].
\end{eqnarray}
	\end{proof}
\end{proposition}
 We note that the length of the signal can be easily derived from the autocorrelation of the signal if the separation condition is met. Therefore, the assumption that $L=1$ and $x[0]$ and $x[L-1]$ are non-zero makes sense.

The heterogeneous case $K>1$ was explored for periodic autocorrelation functions. The aperiodic autocorrelations are the periodic autocorrelations of signals padded by zeros \TODO{we should be prudent here}. Therefore, the following results hold for our setup as well. In~\cite{bandeira2017estimation}. There, it was shown that 
there is a finite list of solutions for $K$ generic signals when 
\begin{itemize}
	\item $K=2$ when $L>1$,
	\item $K=3$ when $L>12$,
	\item $K=4$ when $L>18$,
	\item $5\leq K\leq 15$ when $L\geq 6K-5$.	
\end{itemize}
The authors conjecture that for $K>15$, $L\geq 6K-5$ is enough. Recently, Joe told use that he has proven that there is unique mapping in the same regime.  
This also holds for arbitrary weights $\gamma_i$ which are rational fractions.

If the noise level $\sigma^2$ is known, then for $K=1$, one can estimate $m$ from only the first two moments, namely, with estimation rate of $\sigma^4/N$.
\begin{proposition}
	Let $K=1$. Then, 
	\begin{equation*}
	\frac{M}{N} = \frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
	\end{equation*}
	\begin{proof}
The relation is proved by plugging the definitions of the signal autocorrelations into the right-hand side of the equation~\eqref{eq:autocorrelations}. 	
\end{proof}
\end{proposition}

@@

I DIDN'T SAY ANYTHING ABOUT ESTIMATION RATE

@@

We proceed with the second moment. Let us fix $\ell\in[0,\ldots,L-1]$. Then, we can compute, 
\begin{equation}
\begin{split}
a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell] \\
& \underbrace{\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}},
\end{split}
\end{equation}
where the cross terms between the signal and the noise vanish in the limit.

We treat the signal and noise terms separately. We first break the noise term into $M_N$ different sums, each contains one copy of the signal, and get
\begin{equation}
\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
\end{equation}
Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
\begin{equation}
\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
\end{equation}
Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and therefore converge to zero almost surely as $N\to\infty$.
If $\ell=0$, 
\begin{equation}
\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon[i]^2 \xrightarrow{a.s.} \sigma^2.
\end{equation}

We are now moving to the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2$ and recall that 
\begin{equation*}
a_y^3[\ell_1,\ell_2] = \sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]. 
\end{equation*}
This sum can be broken into eight partial sums. The first contains only signal terms and converges to a $\gamma a_x^3$. Three other partial sums contains the product of two signal entries and one noise term. Since the noise is independent of the signal, then these terms go to zero almost surely.

We next analyze the contribution of triple product of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
\begin{equation*}
\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
\end{equation*}
For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely. This also holds for $\ell_1=\ell_2=0$.

To complete the analysis, we consider the terms including the product of two noise terms and one signal entry. Most of these terms converges to zero almost surely because of interdependency between the noise entries. For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$.

>>>>

If the noise level is negligible, estimating the signals is easy.
One can detect the signal occurrences in the data sequence and then estimate the signals using clustering and averaging.
Even in higher noise level regimes, clever methods based on template matching, such as those used in structural biology~\cite{heimowitz2018apple} and radar~\cite{gogineni2017passive}, may work.
However, in the low signal--to--noise (\SNR) regime, detection of individual signal occurrences is impossible as clarified in Section~\ref{sec:model}. In Figure~\ref{fig:example} we demonstrate an instance of the problem in different noise levels. Figure~\ref{fig:data2D_clean} shows a excerpt of a big image that contains many repetitions of $21\times 21$ small image. The small image is a downsampled version of TKTK, which is shown in Figure~\ref{fig:signal2D_clean}. In Figures~\ref{fig:data2D_noisy_02} and~\ref{fig:data2D_noisy_1} the same excerpt is shown with the addition of i.i.d.\ Gaussian noise with standard deviations of $0.2$ and $1$, respectively.

@@

	\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{signal2D_clean}
	\caption{Clean signal}
	\label{fig:signal2D_clean}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{signal2D_LS_all_images}
	\caption{710K micrographs, $M=561Mega$, error  = $0.05062$}
	\label{fig:signal2D_LS}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{signal2D_LS_exp1}
	\caption{Recovery with 140K micrographs and $M = 110Mega$, error = ? }
	\label{fig:signal2D_RRR}
\end{subfigure}

@@

This work is primely motivated by  innovative technologies for single particle reconstruction, such as cryo-electron microscopy (cryo--EM) and X-ray Free--Electron Laser (XFEL). The acquired data in these modalities is contaminated with high noise levels. Therefore, any molecule reconstruction algorithm must take  the challenging $\SNR$ level into account.  In the last part of this manuscript, we will revisit the cryo--EM problem and draw connections with the estimation problem under consideration.

@@

Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. For each $x_i$, we associate a binary signal  $s_i\in\{0,1\}^N$, referred to as the \emph{support signal} and let $s = \sum_{i=1}^Ks_i$. The non-zero values of $s_i$ indicates the locations of $x_i$ in $y$. If $s_i[n]=1$, then $y[n+j] = x_i[n+j]+\varepsilon[n+j]$ for $j=0,\ldots,L-1$.
We denote the cardinality of $s_i$ by $M_i$  and $M = \sum_{i=1}^{K}M_i$. We do not assume the knowledge of $M_i$'s, neither of $M$.

The support signals are generated by the following generative model. The signal $s$ is initialized with zeros.
First, an index $i_1$ is drawn uniformly from $\{1,\ldots,N\}$ and we set $s[i_1]=1$. A second index $i_2$ is then drawn uniformly from $\{1,\ldots,N\}$. If $\vert i_2-i_1\vert \geq L$,
then we set $s[i_2]=1$, otherwise we keep $s[i_2]=0$ and draw a new index  from uniform distribution. We then proceed adding  non-zero entries to $s$,  while keeping the separation condition until some halting criterion is obtained. Ultimately, each  non-zero value of $s$ is associated with one of the $s_i$'s uniformly over  $\{1,\ldots,K\}$. We note that if the support is sparse enough, this generative model can be approximated by a simple Bernoulli process which takes the values of one and zero with probabilities  $M/N$ and $1-M/N$, respectively.

The simplest way to present the forward model is a mix of blind deconvolution problems between the support signals and the unknown signals
\begin{equation}
y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
\end{equation}
We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
The goal is to estimate $x_1,\ldots,x_K$ from $y$.

Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few. Clearly, without additional information on the signal, blind deconvolution is ill-posed. In our case, the prior information is that $s$ is a binary, sparse, signal. 
Other settings of blind deconvolution problems have been analyzed recently under different settings, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
where the focus is on high $\SNR$ regimes.

In our setup, the support signals $s_1,\ldots,s_K$ are the \emph{latent} variables of the problem. Indeed, in many blind deconvolution applications the goal is merely to estimate one of the unknown signals. For instance, in image deblurring, both the blurring
kernel and the high-resolution image are unknown, but the prime goal is only
to sharpen the image.
If $x$ is known and $K=1$, then  $s$ can be estimated by linear programming  in the high $\SNR$ regime~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}. However, in the low $\SNR$ regime, estimating $s$ is impossible. To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contain one occurrence of $x$. Put it differently, we get a series of windows, each one contains a signal at unknown location.
Estimating the first entry of the signals within each  window is an essentially easier problem the detecting the support of $s$ since the windows are given to us by the oracle. Apparently, this problem, called alignment or synchronization, is impossible in the low $\SNR$ regime.
For instance, the variance of any estimator is, at best, proportional to $\sigma^2$ and independent of the number of windows, even if $x$ is known~\cite{aguerrebere2016fundamental}. Therefore, we conclude that that detecting the non-zero values of $s$ is impossible in low \SNR.

In the next section we show that if $M$ is large enough, then estimating the signals is possible, in any $\SNR$ level and to any accuracy, although we cannot detect their occurrences in $y$.

@@

Our method for estimating the signals relies on two pillars. 
First, we use the autocorrelation functions of the data to estimate a mix (i.e., linear combination) of the $K$ signals autocorrelations. The mixed autocorrelation can be estimated to any accuracy, in any $\SNR$ level, if $M$ is large enough and the separation condition on the support is held. Then, we use least-squares (LS) estimator to estimate the signals from their mixed autocorrelation. From pedagogical reasons, we start with the second stage of recovering signals from their autocorrelations. In this section we mainly discuss the uniqueness of the mapping from the autocorrelation to the signals. Concrete algorithms will be discussed in the next section.

For the purpose of this paper, we need the first three (aperiodic) autocorrelation functions of a signal $z\in\mathbb{R}^W$, defined as
\begin{align} \label{eq:autocorrelations}
a_z^1 &= \sum_{i=0}^{W-1} z[i], \nonumber\\
a_z^2[\ell] &= \sum_{i=0}^{W-1-\ell} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] &= \sum_{i=0}^{W-1-\max\{\ell_1,\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. 
\end{align}
Note that the autocorrelation functions are symmetric so that $a_z^2[\ell] = a_z^2[-\ell]$ and $a_z^3[\ell_1,\ell_2] = a_z^3[-\ell_1,-\ell_2]$.

A one-dimensional signal is determined uniquely by its third-order auto-correlation:
\begin{proposition}
	Suppose that $z[0]$ and $z[L-1]$ are non-zeros. Then, a signal $z\in\mathbb{R}^W$ is determined uniquely from  $a_z^2$ and $a_z^3$.
	\begin{proof}
		From the second-order autocorrelation, we ge
		\begin{equation*}
		a_z^2[L-1] = z[0]z[L-1]\neq 0.
		\end{equation*}
		Then, from the third-order autocorrelation we can compute $z[k]$ for all $k=0,\ldots L-1$ by
		\begin{eqnarray}
		a_z^3[k,L-1] = z[0]z[k]z[L-1].
		\end{eqnarray}
	\end{proof}
\end{proposition}
We note that the length of the signal can be easily derived from the second-order autocorrelation of the signal. Therefore, the assumption that $z[0]$ and $z[L-1]$ is met in practice. We also note that for one-dimensional signals, the second-order autocorrelation does not determined the signals uniquely~\cite{beinert2015ambiguities,bendory2017fourier}. This is not the case for dimensions greater than one, in which almost all signals are determined uniquely from their aperiodic autocorrelations, up to sign (phase in the complex case) and reflection through the origin (with conjugation in the complex case)~\cite{hayes1982reconstruction,hayes1982reducible,bendory2017fourier}. The sign ambiguity can be resolved by the mean of the signal if it is not zero. However,  in order to determine the reflection symmetry ($Z_2$ symmetry), one needs to use the third moment.

The heterogeneous case $K>1$ was explored for periodic autocorrelation functions. The aperiodic autocorrelations are the periodic autocorrelations of signals padded by zeros. Therefore, the following results hold for our setup as well  \TODO{we should be prudent here to make sure that this set does not ``fall'' in the zero measure}. In~\cite{bandeira2017estimation}, it was shown that a mix of $K$ third-order autocorrelations determine  a finite list of $K$ generic signals when 
\begin{itemize}
	\item $K=2$ when $L>1$,
	\item $K=3$ when $L>12$,
	\item $K=4$ when $L>18$,
	\item $5\leq K\leq 15$ when $L\geq 6K-5$.	
\end{itemize}
The authors conjecture that for $K>15$, $L\geq 6K-5$ is enough. Recently, Joe told use that he has proven that there is unique mapping in the same regime.  
This also holds for arbitrary weights $\gamma_i$ which are rational fractions.

\TODO{Where we should refer to Gianakis's paper?}

We are moving forward to discuss the second question of how to estimate the autocorrelation of the signals from the data. 
The analysis is conducted in the asymptomatic regime where $M_1,\ldots,M_K,N\to\infty$. We define the ratios 
\begin{equation}
\gamma_i = \frac{M_i L}{N},
\end{equation}
and $\gamma = \sum_{i=1}^K\gamma_i$.
Under the separation condition, we have $\gamma\leq\frac{L}{2L-1}\approx 1/2$.
The main insight is that if $s$ satisfies the separation condition, then the first $L$ entries of the data autocorrelations converge to a $\gamma$ scaled version of a mix of the signals autocorrelations:
\begin{align}
\lim_{N\to\infty} a_y^1 &= \sum_{i=1}^K\gamma_i a_{x_i}^1, \\
\lim_{N\to\infty} a_y^2[\ell] &= \sum_{i=1}^K\gamma_i a_{x_i}^2[\ell] +\sigma^2\delta[\ell],\\
\lim_{N\to\infty} a_y^3[\ell_1,\ell_2] &= \sum_{i=1}^K\gamma_i a_{x_i}^3[\ell_1,\ell_2] + \sigma^2\left(\sum_{i=1}^K\gamma_i a_{x_i}^1\right)(\delta[\ell_1,0]+\delta[0,\ell_2]+\delta[\ell_1,\ell_2]),
\end{align}
for $\ell,\ell_1,\ell_2=0,\ldots L-1$.
These relations are proved in Appendix~\ref{sec:autocorrelation_computation}. The analysis is similar to~\cite{bendory2017bispectrum,boumal2017heterogeneous}, yet a special caution should be taken with the noise dependencies. This means that given $M_1,\ldots,M_K$ and $\sigma^2$ and $K$ does not exceed the limit for uniqueness, the one can estimate the signals from the third-order autocorrelation of the data. In other words, the signals can be estimated in asymptotic estimation rate of $\sigma^6/N$.

If the noise level $\sigma^2$ is known, then for $K=1$, one can estimate $M$ from only the first two moments, namely, with estimation rate of $\sigma^4/N$.
\begin{proposition}
	Let $K=1$. Then, 
	\begin{equation*}
	\frac{M}{N} = \frac{(a^1_y)^2}{\sum_{j=0}^{L-1}a_y^2[j]-\sigma^2}.
	\end{equation*}
	\begin{proof}
The relation is proved by plugging the definitions of the signal autocorrelations into the right-hand side of the equation~\eqref{eq:autocorrelations}. 	
\end{proof}
\end{proposition}

@@

Estimating $\sigma$ and $M$?

@@

We proceed with the second moment for fixed $\ell\in[0,\ldots,L-1]$. Then, we can compute, 
\begin{equation}
\begin{split}
a_y^2[\ell] & = \frac{1}{N}\sum_{i=0}^{N-1-\ell}y[i]y[i+\ell] \\
& \underbrace{\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell]}_{\text{signal term}} + \underbrace{\frac{1}{N}\sum_{i=0}^{N-1}\varepsilon[i]\varepsilon[i+\ell]}_{\text{noise term}},
\end{split}
\end{equation}
where the cross terms between the signal and the noise almost surely vanish in the limit.

We treat the signal and noise terms separately. We first break the signal term into $M_N$ different sums, each contains one copy of the signal, and get
\begin{equation} \label{eq:2nd_moment_signal_term}
\frac{1}{N}\sum_{j=1}^{M_N}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \frac{M_NL}{N}\frac{1}{L}\sum_{i=0}^{L-\ell-1}x[i]x[i+\ell] = \gamma a_x^2[\ell].
\end{equation}
Similarly, for $\ell\neq 0$, we can break the noise term into a sum of independent terms 
\begin{equation}
\frac{1}{N}\sum_{i=0}^{N-1-\ell} \varepsilon[i]\varepsilon[i+\ell] = \frac{1}{\ell}\sum_{i=0}^{\ell-1}\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i].
\end{equation}
Each term of $\frac{1}{N/\ell}\sum_{j=0}^{N/\ell -1} \varepsilon[j\ell + i] \varepsilon[(j+1)\ell + i]$ is an average of $N/\ell$ independent terms with expectation zero, and therefore converge to zero almost surely as $N\to\infty$.
If $\ell=0$, 
\begin{equation}
\frac{1}{N}\sum_{i=0}^{N-1} \varepsilon[i]^2 \xrightarrow{a.s.} \sigma^2.
\end{equation}

We are now moving to the third-order autocorrelation. Let us fix $\ell_1\geq\ell_2$ and recall that 
\begin{equation*}
a_y^3[\ell_1,\ell_2] = \sum_{i=0}^{N-1-\ell_1} y[i]y[i+\ell_1]y[i+\ell_2]. 
\end{equation*}
Writing explicitly in terms of signal and noise, this sum can be broken into eight partial sums. The first contains only signal terms and converges to $\gamma a_x^3$ from the same reasons as~\eqref{eq:2nd_moment_signal_term}. Three other partial sums contain the product of two signal entries and one noise term. Since the noise is independent of the signal, then these terms go to zero almost surely.

We next analyze the contribution of triple product of noise terms. For $\ell_1\neq 0$, this sum can be formulate as follows:
\begin{equation*}
\sum_{i=0}^{N-1-\ell_1} \varepsilon[i]\varepsilon[i+\ell_1]\varepsilon[i+\ell_2] = \frac{1}{\ell_1}\sum_{i=0}^{\ell_1-1}\frac{1}{N/\ell_1}\sum_{j=0}^{N/\ell_1 -1 }\varepsilon[j\ell_1+i]\varepsilon[(j+1)\ell_1+i]\varepsilon[j\ell_1+i+\ell_2].
\end{equation*}
For each fixed $i$, we sum of over $N/\ell_1$ independent variables that goes to zero almost surely. For $\ell_1=\ell_2=0$, we get a some of $N$ independent variables, each is a triple product of Gaussian variables with zero mean. Therefore, it is also converges to zero.

To complete the analysis, we consider the three terms composed of the product of two noise terms and one signal entry. Most of these terms converges to zero almost surely because of interdependency between the noise entries. For $\ell_1=0, \ell_2=0$ and $\ell_1=\ell_2$,  a simple computation shows that the sum converges to $\gamma\sigma^2a_x^1$.
